Followers Are Not Enough: A Multifaceted Approach to Community Detection in Online Social Networks

### 2014-11-25 paper-postreview/response-to-editor.txt

Reviewer 1
==========

- The authors claim that the novelty of their work is based on the fact that community extraction has been done "blindly", i.e. without considering that actual type of network under analysis. It seems to the reviewer that this is simply not true, because the construction of the network is always done considering a specific representation of the problem under consideration. A link can represent an activity, an interaction, etc.

*

- In particular, as far as the activity-based approach is concerned, the definition of influence is very difficult to justify. The method itself is not particularly new. It was used in the past in [44]. In general, in my opinion, the use of transfer entropy for measuring the influence of a certain user on another user is fairly questionable. In fact, saying that a certain user influences another one considering th patterns of user activity might be rather questionable. What about different "followees" influencing the same person? What about external influences? In any case, I think that it is difficult to talk about "influence" in these cases. And then there is a fundamental question: it is not clear which information you can get using transfer entropy and its semantics.

*

- Also, the similarity based on topics is not a contribution per se in my opinion. Topic extraction techniques (also in more refined ones, as cited by the authors) have been used in several papers.

* As far as the evaluation is concerned, in Section 3.2 the authors compare their results by comparing the communities for different types of network structure. But, by doing this, the authors do not actually evaluate if their question based method is actually able to provide an "answer" considering the semantics of the question. I believe that a method based on a given semantics should be able to provide an answer to the question that is asked.

- "many of these connections do not correspond to real friendships or more generally to accounts that users interact with": This sentence is very difficult to understand. People in Twitter follow accounts that are not real friends, but news outlets, governmental organizations, etc.

*

- "structural communities": also these are structural communities based on a different type of weight.

*

- "we show that the communities obtained in the three weighted cases are highly different from each other": this is a fairly result. Different weights lead to different results.

*

- "contact filtering": this is not a common term/concept at all in my opinion. It seems that tit has been introduce by the authors.

*

- "However, with the prevalence of large rich data sets for online social networks": I think that the opposite is actually true. Sociologists usually go beyond simple structure and/or structure is used to describe dynamics.

*

- "On a more abstract level, a user might consider themselves part of a community of people discussing similar topics...": this is a standard approach to social network analysis. The membership is defined by the users themselves.

*

- "Interaction-based": why is this different from activity based? It seems to me that this is a sort of limit case of the "activity-based" considering a simplification of the problem: communication vs no communication.

*

- "We divide our approaches into four categories": I think that this is not strictly necessary since you have already mentioned this.

*

- "However, we conjecture": rightly, the authors say that this is just a conjecture. At the same time, very bold claims are based on this very simple conjecture.

*

- "For example [6],": the idea of building a network based on this is not particularly new.

*

- "However, this approach focused on data for a particular topic...": this is not a credible justification to dismiss the work. The fact that you present an approach based on structure together with this one does not represent a significant contribution per se in my opinion.

*

- The discussion of the selection of the clustering algorithm can be summarized in my opinion.

*

- "For this reason, we coarsen each time series by considering non-overlapping time intervals...": this time series might be rather sparse. A discussion of this issue might be helpful.

*

- "A positive value for the transfer...": this is just an assumption, you should say that you assume this.

*

- Formulae (2) and (3): you should use a different symbol for p in (2) and (3). In (4) the p can be very different. This formula is not correct in my opinion.

*

- In general, the 3 metrics listed in (2), (3) and (4) are not properly motivated in my opinion.

*

- Section 2.5: the extraction of the weights is pretty standard, I do not consider this as a contribution per se.

*

- The result in Figure 1 is not really significant. These are comparisons between different methods without a clear interpretation of the results.

*

- "That is, the transfer entropy coverings are more similar...": These findings are not particularly insightful in my opinion. These might be just artifacts of the definitions.

*

- Figure 2: I cannot se real insights from these plots.

*

- For meaningful community structure...:: It is not clear to me why this should be the case. You can have in theory similar communities. This is probably not the case, but you should avoid to say that you expect this behaviour.

*

- "If the community structure were arbitrary...": this is not true in general.

*

- "Similarly, for the coverings corresponding to...": it is not possible to compare these results directly, since they represent very different properties. They are not really normalized/scaled up.

*

- "This means that these accounts had high influence...": this is a strong claim. This might be simply due to the higher probability of retweet for that account, i.e., the use of the entropy transfer function might not necessary. The actual introduction of such a complex tool for describing this tool is not completely justified.

*

- "Lastly, it is interesting to note...": the same might be true for these accounts.

*

- "even activity-based influence": it depends, you can consider weights accordingly, for example based on the frequency/intensity of the interaction, etc. You can even add a weight using Granger correlation. You can put a weight if the correlation is higher than a certain given threshold for example - and only tnen apply the community detection algorithm.

*

- "erroneous results": how can you say that your resutls are corrects.

*

Reviewer 2
==========

- My only minor complaint is the following. Depending on the "type" of links considered, I expect the network to be different. Why did the authors focus only on communities, instead of considering also more basic network properties? I would add some statistics about it.

*

### 2014-11-25 paper-postreview/response-to-editor.txt

Reviewer 1
==========

- The authors claim that the novelty of their work is based on the fact that community extraction has been done "blindly", i.e. without considering that actual type of network under analysis. It seems to the reviewer that this is simply not true, because the construction of the network is always done considering a specific representation of the problem under consideration. A link can represent an activity, an interaction, etc.

* We did not mean to claim that the community extraction was done blindly. In fact, we demonstrated exactly the opposite: by intentionally choosing a different question about the individuals in the social network, very different community structure may be extracted. We did wish to highlight that a question-oriented approach to community detection can be undertaken with the network at-hand, assuming the network was collected in a way that would not strongly bias any of the weighting metrics we utilized.

* The method used in [44] is very different from our own. We originally cited this paper because it was the impetus for us considering point process-type models of user behavior in social media, but we see that this may have been misleading. The method in [44] assumes a weighted adjacency matrix based on the point-wise (in time) informational coherence between any two nodes in the network. The informational coherence is computed as the normalized mutual information between the marginal causal states associated with each node in the vertex, and thus measures whether or not the information processing between any two nodes is associated across time. Thus, this measure is neither directed, nor does it account for lagged effects in terms of the interaction between two nodes in network, as our method does.

* We do not believe that the contribution of our paper is any of the particular weightings, but rather in how the choice of a weighting can strongly impact. We sought to include simple, reasonable metrics motivated by the interaction-, topic-, and activity-based questions, but did not intend for these to be new or even state-of-the-art.

- As far as the evaluation is concerned, in Section 3.2 the authors compare their results by comparing the communities for different types of network structure. But, by doing this, the authors do not actually evaluate if their question based method is actually able to provide an "answer" considering the semantics of the question. I believe that a method based on a given semantics should be able to provide an answer to the question that is asked.

### 2014-11-25 paper-postreview/response-to-editor.txt

- Also, the similarity based on topics is not a contribution per se in my opinion. Topic extraction techniques (also in more refined ones, as cited by the authors) have been used in several papers.

* We do not believe that the contribution of our paper is any of the particular weightings, but rather in how the choice of a weighting can strongly impact. We sought to include simple, reasonable metrics motivated by the interaction-, topic-, and activity-based questions, but did not intend for these to be new or even state-of-the-art.

- As far as the evaluation is concerned, in Section 3.2 the authors compare their results by comparing the communities for different types of network structure. But, by doing this, the authors do not actually evaluate if their question based method is actually able to provide an "answer" considering the semantics of the question. I believe that a method based on a given semantics should be able to provide an answer to the question that is asked.

* We have attempted to address this point more fully in section 3.4 of the revised manuscript. In particular, we demonstrate how the topic-based, interaction-based, and activity-based networks give rise to meaningful communities based on their respective interpretations of the meaning of 'community.' e.g. A topic-based community based around small businesses, an activity-based community based around individuals in Denver, CO, etc. Finally, we have added individual case studies to demonstrate how the community membership of a user across the different community types reveals different aspects of the user's online identity.

@@

- "many of these connections do not correspond to real friendships or more generally to accounts that users interact with": This sentence is very difficult to understand. People in Twitter follow accounts that are not real friends, but news outlets, governmental organizations, etc.

* Thank you for this suggestion. We have revised this sentence to more accurately reflect the plurality of account-types that exist on Twitter.

@@

- "we show that the communities obtained in the three weighted cases are highly different from each other": this is a fairly result. Different weights lead to different results.

* The fact that different weightings should give rise to different communities is in our opinion non-trivial. For example, if all of the different weightings were strongly associated with each other, then we would expect to obtain the same communities, since the same structural backbone was used to to construct each weighted network. One might expect this to be the case with, for example, the interaction-based and activity-based weights. However, as both Figures 1 and 2 demonstrate, this is not the case.

@@

- "contact filtering": this is not a common term/concept at all in my opinion. It seems that tit has been introduce by the authors.

* We did not introduce the term/concept. It can be found in reference [5].

@@

- "However, with the prevalence of large rich data sets for online social networks": I think that the opposite is actually true. Sociologists usually go beyond simple structure and/or structure is used to describe dynamics.

* We did not mean to claim that sociologists currently take this approach, but rather that this approach was more reasonable in the era of small-scale studies of human/human interaction (for example, the small-world experiment of Stanley Milgram, or Zachary's Karate club).

@@

- "Interaction-based": why is this different from activity based? It seems to me that this is a sort of limit case of the "activity-based" considering a simplification of the problem: communication vs no communication.

* [[Josh]]

- "We divide our approaches into four categories": I think that this is not strictly necessary since you have already mentioned this.

* Thank you for this suggestion. We have revised the manuscript to remove this redundancy.

@@

- "However, we conjecture": rightly, the authors say that this is just a conjecture. At the same time, very bold claims are based on this very simple conjecture.

* We agree that our original presentation of transfer entropy did not do a good enough job of stressing the difference between social and information theoretic influence. We have attempted to revise our presentation of transfer entropy to make it more clear exactly what we believe transfer entropy does and does not capture in the setting of our paper.

@@

- "For example [6],": the idea of building a network based on this is not particularly new.

* We agree. As stated above, we feel that our contribution with this paper is not to demonstrate new ways to construct networks from data derived from Twitter, but rather how to use many of those networks to highlight the multifaceted nature of user engagement with online social media.

@@

- "For this reason, we coarsen each time series by considering non-overlapping time intervals...": this time series might be rather sparse. A discussion of this issue might be helpful.

* [[Josh]]

- "A positive value for the transfer...": this is just an assumption, you should say that you assume this.

* We have revised the manuscript to emphasize that this is a property that immediately follows from the definition of the transfer entropy, rather than an assumption that we have made. However, we admit that our interpretation of the positivity is an assumption, and we have attempted to make this interpretation more concrete in the revised manuscript.

@@

- Formulae (2) and (3): you should use a different symbol for p in (2) and (3). In (4) the p can be very different. This formula is not correct in my opinion.

* Thank you for this suggestion. The p was not meant to be a variable, but rather to indicate the proportion of retweets / mentions. We have revised our notation to remove any confusion caused by the use of the prefix p.

@@

- In general, the 3 metrics listed in (2), (3) and (4) are not properly motivated in my opinion.

* [[Elisa]]

- Section 2.5: the extraction of the weights is pretty standard, I do not consider this as a contribution per se.

* As noted in previous responses, the scope of this paper was not to present new weighting metrics, but rather to demonstrate the impact of standard weighting metrics on the communities extracted from a real-world online social network.

@@

- The result in Figure 1 is not really significant. These are comparisons between different methods without a clear interpretation of the results.

* We believe that the differing distributions do demonstrate that the mesoscopic structure of the network looks different depending on the question-type employed to extract the communities. For example, using the follower network alone results in smaller communities that resolve together into larger communities after applying the weightings. Thus, those individuals who appear to be unassociated based on the follower network become associated after we include more information about their activity / interactions / topic profiles.

@@

- Figure 2: I cannot se real insights from these plots.

*

- For meaningful community structure...:: It is not clear to me why this should be the case. You can have in theory similar communities. This is probably not the case, but you should avoid to say that you expect this behaviour.

* Thank you for pointing this out. We have revised the manuscript to emphasize those cases when we do / do not expect the edge weight distributions to vary depending on the conditioning.

@@

- "If the community structure were arbitrary...": this is not true in general.

* Thank you for pointing this out. We have revised the manuscript to account for this.

@@

- "Lastly, it is interesting to note...": the same might be true for these accounts.

* [[Josh]]

- "even activity-based influence": it depends, you can consider weights accordingly, for example based on the frequency/intensity of the interaction, etc. You can even add a weight using Granger correlation. You can put a weight if the correlation is higher than a certain given threshold for example - and only tnen apply the community detection algorithm.

* We agree. Alternative activity-based metrics could and should certainly be applied. In this sentence, we meant to emphasize that the structural network alone would not capture this information, and therefore performing influence detection using this network might lead to

@@

- "erroneous results": how can you say that your resutls are corrects.

* We have expanded on this point in the revised manuscript, and given examples of how influence detection based solely on the structural network could result in an incomplete understanding of the influence exhibited by users in an online social network.

@@

Reviewer 2
==========

- My only minor complaint is the following. Depending on the "type" of links considered, I expect the network to be different. Why did the authors focus only on communities, instead of considering also more basic network properties? I would add some statistics about it.

* Thank you for this suggestion. We decided to focus the paper on communities, and felt that going into more detail about the differences in other network properties went beyond the scope of our analysis. However, as we indicated in the Future Work section, we believe that such investigations could yield new insights into the multifaceted nature of online social networks.

### 2014-11-26 paper-postreview/intro.tex
Took a pass through the paper.
I made minor changes, mostly stylistic.

Because of the importance of structural networks in online social media, a large amount of work in this area has focused on using structural networks for community detection. In this traditional view, `community' is defined as a collection of nodes (users) within the network which are more highly connected to each other than to nodes (users) outside of the community 
%Here, by `community' we mean the standard definition from the literature on social networks: a collection of nodes (users) within the network which are more highly connected to each other than to nodes (users) outside of the community
~\cite{girvan2002a, newman2004finding}. For instance, in~\cite{java2009we}, the authors use a follower network to determine communities within Twitter, and note that conversations tend to occur within these communities. The approach of focusing on the structure of networks makes sense for `real-world' sociological experiments, where obtaining additional information about user interactions may be expensive and time-consuming. However, with the prevalence of large, rich data sets for online social networks, additional information beyond the structure alone may be incorporated, and these augmented networks more realistically reflect how users interact with each other on social media services~\cite{nguyen2011adaptive},~\cite{grabowicz2012social}.

@@

\item Ask \emph{several} questions about the communities that may be present in the network, each of which is aimed at revealing a new facet of the community present in the network---{\it e.g.,} which users are tightly connected structurally? which groups of users have similar topical interests?

\item Derive a weighting scheme aimed at answering each of the questions asked in the first step and then perform community detection on each weighted network.
\item Compare the disjoint \emph{and} overlapping communities that arise from this series of experiments on a micro and macro scale to unveil all the interesting facets of community present in the social network. 
\end{enumerate}

This is especially true for social network analysis. In social networks, a `community' could refer to several possible structures. The simplest definition of community, as we have seen, might stem from the network of explicit connections between users on a service (friends, followers, etc.). On small time scales, these connections are more or less static, and we might instead determine communities, as is standard in the literature\alert{david or elisa can you add some citations please}\cite{}, based on who is talking to whom or which users talk about similar topics, providing a more dynamic picture of community.
More abstractly, we could even define communities as groups of people who exhibit similar activity profiles. We can characterize these types of communities based on the types of questions we might ask about them:
\begin{itemize}
	\item \textbf{Structure-based:} Who are your stated friends? Whom do you follow?
	\item \textbf{Activity-based:} Who shares similar activity profiles?
	\item \textbf{Topic-based:} What do you talk about?
	\item \textbf{Interaction-based:} Whom do you communicate with?
\end{itemize}

This is not meant to be an exhaustive list, but rather a list of some of the more common types of communities observed and studied in social networks. Instead of looking at each of these questions in isolation---which is the standard approach---we propose looking at when, why, and how communities motivated by these different questions overlap and are disjoint, and whether different approaches to asking the question, ``What community are you in?'' leads to different insights about a social network. For example, a user on Twitter might connect mostly with computational social scientists, utilize the service nearly every time a particular user or group of users is active, talk mostly about machine learning, and interact solely with close friends (who may or may not be computational social scientists). 
For this user, the answers to each question therefore correspond to more or less distinct communities. By contrast, a teenage user may only connect and interact with their friends, will most likely exhibit similar activity patterns dictated by the academic and extracurricular schedule of a student. For this user, the answers to each question map to the same community of users.
Thus, each question acts to highlight a particular `profile' of a user, and these profiles can help identify the ways in which a user interacts with and like other users in their online social network. 
We now consider in more detail how each of these types of questions motivates a question-specific community. Later in Section~\ref{sec:conc} we will show how asking \emph{all} of these questions---instead of focusing on only one---gives a much deeper multifaceted view of the overlapping \emph{and} disjoint communities that users belong to.

Na\"ively the activity-based approach is motivated by the question of ``Which users in a network have similar activity profiles?"
%--- \emph{i.e.,} which user(s) cause groups of users to become active on the network.  %, \emph{i.e.}, which user(s) cause a user(s) to interact with the network. 
 With this question in mind, a community can then be thought of as those users who use (or do not use) the service at similar times. However, the measure we use is slightly more subtle that this. In particular, these communities can be thought of as groups of users who possess so-called ``predictive capacity" with one another, i.e., given a user $u$ and follower $f$ who are members of a community detected with this weighting, there exists a reduction in uncertainty about the activity profile of follower $f$ (tweeting or remaining silent), given the tweet history of user $u$.

@@

According to~\cite{ver2012information} a positive transfer entropy between a user $u$ and a follower $f$ indicates that $u$ ``influences" $f$, or that $u$ and $f$ share a common influencer. We would like to point out however that we are skeptical whether this measure truly captures social influence in its entirety. We instead treat this weighting as a way to explicitly quantify a reduction in uncertainty of whether a follower $f$ will be active or not given the tweet history of a user $u$. This provides an information theoretic framework in which we can capture communities with predictive capacity between users or users with similar activity profiles. We call this relation ``PV-AC". As an aside, while we are skeptical that this measure can capture social influence, later in this paper we show that this information theoretic measure agrees with other concepts of influence such as the Forbes list of ``Top 10 Social Media Influencers" and corroborates with the so-called strength of weak ties~\cite{granovetter1973strength}. Even so, we do not explicitly treat---and we do not believe it should be treated---as a quantification of social influence. Instead this measure should be treated merely as a way to suggest users with casually related (in a Granger sense) tweet histories, i.e., users with similar activity profiles (PV-AC).

>>>>

Because of the importance of structural networks in online social media, a large amount of work in this area has focused on using structural networks for community detection. In this traditional view, a community is defined as a collection of nodes (users) within the network which are more highly connected to each other than to nodes (users) outside of the community 
%Here, by `community' we mean the standard definition from the literature on social networks: a collection of nodes (users) within the network which are more highly connected to each other than to nodes (users) outside of the community
~\cite{girvan2002a, newman2004finding}. For instance, in~\cite{java2009we}, the authors use a follower network to determine communities within Twitter, and note that conversations tend to occur within these communities. The approach of focusing on the structure of networks makes sense for `real-world' sociological experiments, where obtaining additional information about user interactions may be expensive and time-consuming. However, with the prevalence of large, rich data sets for online social networks, additional information beyond the structure alone may be incorporated, and these augmented networks more realistically reflect how users interact with each other on social media services~\cite{nguyen2011adaptive},~\cite{grabowicz2012social}.

@@

\item Ask \emph{several} questions about the communities that may be present in the network, each of which is aimed at revealing a new facet of the community structure present in the network---{\it e.g.,} which users are tightly connected structurally? which groups of users have similar topical interests?

\item Derive a weighting scheme aimed at answering each of the questions asked in the first step and then perform community detection on each weighted network.
\item Compare the disjoint \emph{and} overlapping communities that arise from this series of experiments on a micro and macro scale to unveil all the interesting facets of community structure present in the social network. 
\end{enumerate}

This is especially true for social network analysis. In social networks, a `community' could refer to several possible structures. The simplest definition of community, as we have seen, might stem from the network of explicit connections between users on a service (friends, followers, etc.). On small time scales, these connections are more or less static. To form a more dynamic picture of community structure, we might instead determine communities based on who is talking to whom or which users talk about similar topics.
More abstractly, we could even define communities as groups of people who exhibit similar activity profiles. We can characterize these types of communities based on the questions that motivate them:
\begin{itemize}
	\item \textbf{Structure-based:} Who are your stated friends? Whom do you follow?
	\item \textbf{Activity-based:} Who shares similar activity profiles?
	\item \textbf{Topic-based:} What do you talk about?
	\item \textbf{Interaction-based:} Whom do you communicate with?
\end{itemize}

This is not meant to be an exhaustive list, but rather a list of some of the more common types of communities observed and studied in social networks. Instead of looking at each of these questions in isolation---which is the standard approach---we propose looking at when, why, and how communities motivated by these different questions overlap and are disjoint, and whether different approaches to asking the question, ``What community are you in?'' leads to different insights about a social network. For example, a user on Twitter might connect mostly with computational social scientists, utilize the service nearly every time a particular user or group of users is active, talk mostly about machine learning, and interact solely with close friends (who may or may not be computational social scientists). 
For this user, the answers to each question therefore correspond to more or less distinct communities. By contrast, a teenage user may only connect and interact with their friends, will most likely exhibit similar activity patterns dictated by the academic and extracurricular schedule of a student, and will discuss topics typical of their demographic. For this user, the answers to each question map to the same community of users.
Thus, each question acts to highlight a particular `profile' of a user, and these profiles can help identify the ways in which a user interacts with and like other users in their online social network. 
We now consider in more detail how each of these types of questions motivates a question-specific community. Later in Section~\ref{sec:conc} we will show how asking \emph{all} of these questions---instead of focusing on only one---gives a much deeper view of the overlapping \emph{and} disjoint communities that users belong to.

Na\"ively the activity-based approach is motivated by the question of ``Which users in a network have similar activity profiles?"
%--- \emph{i.e.,} which user(s) cause groups of users to become active on the network.  %, \emph{i.e.}, which user(s) cause a user(s) to interact with the network. 
 With this question in mind, a community can then be thought of as those users who use (or do not use) the service at similar times. However, the measure we use is slightly more subtle that this. In particular, these communities can be thought of as groups of users who possess so-called ``predictive capacity" with one another, \emph{i.e.}, given a user $u$ and follower $f$ who are members of a community detected with this weighting, there exists a reduction in uncertainty about the activity profile of follower $f$ (tweeting or remaining silent), given the tweet history of user $u$.

@@

According to~\cite{ver2012information} a positive transfer entropy between a user $u$ and a follower $f$ indicates that $u$ ``influences" $f$, or that $u$ and $f$ share a common influencer. We would like to point out however that we are skeptical whether this measure truly captures social influence in its entirety. We instead treat this weighting as a way to explicitly quantify a reduction in uncertainty of whether a follower $f$ will be active or not given the tweet history of a user $u$. This provides an information theoretic framework in which we can capture communities with predictive capacity between users or users with similar activity profiles. We call this relation ``PV-AC". As an aside, while we are skeptical that this measure can capture social influence, later in this paper we show that this information theoretic measure agrees with other concepts of influence such as the Forbes list of ``Top 10 Social Media Influencers" and corroborates with the so-called strength of weak ties~\cite{granovetter1973strength}. Even so, we do not explicitly treat transfer entropy---and we do not believe it should be treated---as a quantification of social influence. Instead this measure should be treated merely as a way to suggest users with casually related (in a Granger sense) tweet histories, i.e., users with similar activity profiles (PV-AC).

### 2014-11-26 paper-postreview/methods.tex
Took a pass through the paper.
I made minor changes, mostly stylistic.

\section{Methodology}

In the following sections, we introduce the problem of community detection, and present the data set used for our analyses. We then describe our methodology for constructing the question-specific networks. In particular, we introduce an information theoretic statistic for activity-based communities, a retweet-mention statistic for interaction-based communities, and a hashtag similarity metric for defining topic-based communities.

@@

As discussed in the introduction, we adopt the standard definition of \emph{community}: a collection of nodes (users) within a network who are more densely connected to each other than with the rest of the network. Structural community detection is a well studied problem and several different methods and algorithms have been proposed. For a complete review of this subject we refer the reader to \cite{porter2009communities, fortunato2010community}. In this paper however we focus on a class of networks and communities that is far less studied, in particular we study networks which are both \textit{weighted} and \textit{directed} and communities within those weighted directed networks that can (but need not) \emph{overlap}. When selecting a detection algorithm we propose that all three (weight, direction, and overlap) are important for the following reasons. First, communication on Twitter occurs in a directed manner, with users broadcasting information to their followers. An undirected representation of the network would ignore this fact, and could lead to communities composed of users who do not actually share information. Second, we are interested in not just the structure of links but also in their function, and to capture this we use edge weightings which must be incorporated into the community detection process. Finally, since people can belong to multiple and possibly overlapping social (e.g., college friends, co-workers, family, etc.) and topical (e.g., a user can be interested in both cycling and politics and use the network to discuss the two topics with the two different communities) communities, we are interested in finding \textit{overlapping} communities, rather than partitions of the weighted directed network. 
%For example, users can belong to multiple social groups such as college friends, %co-workers, family, etc. and these groups may but need not overlap. A user can also %belong to multiple topical communities, e.g., a user can be interested in both %cycling and politics and use the network to discuss the two topics with the two %different communities.

This last criterion in particular poses a problem because the majority of community detection algorithms developed so far are built to find partitions of a network and few are aimed at finding overlapping communities \cite{Aicher26062014,BaumesGKMP05,PalEtAl05,ZhaWanZha07,Gre07,PhysRevE.77.016107,Lancichinetti2009,PhysRevE.80.016105,Kovacs2010}. Among these methods, even fewer deal with directed or weighted networks. For example, the work of~\cite{PalEtAl05} on clique percolation can account for both features, but not at the same time. A recent method proposed in~\cite{LancichinettiPlos}, OSLOM (Order Statistics Local Optimization Method), is one of the first methods  able to deal with all of these features simultaneously. This method of Lancichinetti et al. relies on a fitness function that measures the statistical significance of clusters with respect to random fluctuations, and attempts to optimize this fitness function across all clusters. 
Following~\cite{LancichinettiPlos}, the significance measure is defined as the probability of finding the cluster in a network without community structure. The null model used is basically the same as the one adopted by Newman and Girvan in \cite{newman2004finding} to define modularity, {\it i.e.} it is a model that generates random graphs with a given degree distribution. The authors tested their algorithm on different benchmarks (LFR and Girvan-Newman) and real networks (such as the US air transportation and the word association network), and compared its performance against the best algorithms
currently available (i.e the ones mentioned in the introduction), and found excellent results. Moreover, they showed that OSLOM is also able to recognize the absence, and not simply the presence, of community structure, by testing it on random graphs. This feature of the algorithm plays an important role in the analysis of real data networks, since it is not always the case that a community structure is indeed present and it is therefore useful to be able to detect its absence too. 
Therefore, given its versatility and performance with benchmark networks, in this paper we used OSLOM to detect \emph{overlapping} communities present in our \emph{weighted} and \emph{directed} networks.
%For this paper we use OSLOM since it allowed us to detect \emph{overlapping} communities present in our \emph{weighted} and \emph{directed} network, and its authors showed that it performs very well on various types of artificial benchmark graphs and also on several real networks.

@@

Operationally, we expect users to interact with Twitter on a human time scale, and thus the natural one-second time resolution is too fine; since most humans do not write tweets on the time scale of seconds. For this reason, we coarsen each time series by considering non-overlapping time intervals ten minutes in length. For each time interval, we record a 1 if the user has tweeted during that time interval, and a 0 if they have not. Thus, the new coarsened time series now captures whether or not the user has been active on Twitter over any given ten minute time interval in our data set. It should be noted that, as (most) users are not constantly tweeting, these time series are quite sparse. This sparsity will skew the distribution of tweet activity toward being inactive, as the distribution should be to reflect realistic interaction patterns. However, if this measure is to be used in practice a deeper analysis of the effects of binning, the resulting sparsity and their role in the activity-based community structure should be carried out.

>>>>

\section{Methodology}
In the following sections, we introduce the problem of community detection, and present the data set used for our analyses. We then describe our methodology for constructing the question-specific networks. In particular, we introduce an information theoretic statistic for activity-based communities, a retweet-mention statistic for interaction-based communities, and a hashtag similarity metric for defining topic-based communities. It should be noted that our goal is to choose representative weightings for each community type so that we may compare community structure across types, and not to introduce novel weighting schemes \emph{per se}.

@@

As discussed in the introduction, we adopt the standard definition of \emph{community}: a collection of nodes (users) within a network who are more densely connected to each other than with the rest of the network. Structural community detection is a well studied problem and several different methods and algorithms have been proposed. For a complete review of this subject we refer the reader to \cite{porter2009communities, fortunato2010community}. In this paper however we focus on a class of networks and communities that is far less studied, in particular we study networks which are both \textit{weighted} and \textit{directed} and communities within those weighted directed networks that can (but need not) \emph{overlap}. When selecting a detection algorithm we propose that all three (weight, direction, and overlap) are important for the following reasons. First, communication on Twitter occurs in a directed manner, with users broadcasting information to their followers. An undirected representation of the network would ignore this fact, and could lead to communities composed of users who do not actually share information. Second, we are interested in not just the structure of links but also in their function, and to capture this we use edge weightings which must be incorporated into the community detection process. Finally, since people can belong to multiple and possibly overlapping social (e.g., college friends, co-workers, family, etc.) and topical (e.g., a user can be interested in both cycling and politics and use the network to discuss the two topics with the two different groups of users) communities, we are interested in finding \textit{overlapping} communities, rather than partitions of the weighted directed network. 
%For example, users can belong to multiple social groups such as college friends, %co-workers, family, etc. and these groups may but need not overlap. A user can also %belong to multiple topical communities, e.g., a user can be interested in both %cycling and politics and use the network to discuss the two topics with the two %different communities.

This last criterion in particular poses a problem because the majority of community detection algorithms developed so far are built to find partitions of a network and few are aimed at finding overlapping communities \cite{Aicher26062014,BaumesGKMP05,PalEtAl05,ZhaWanZha07,Gre07,PhysRevE.77.016107,Lancichinetti2009,PhysRevE.80.016105,Kovacs2010}. Among these methods, even fewer deal with directed or weighted networks. For example, the work of~\cite{PalEtAl05} on clique percolation can account for both features, but not at the same time. A recent method proposed in~\cite{LancichinettiPlos}, OSLOM (Order Statistics Local Optimization Method), is one of the first methods  able to deal with all of these features simultaneously. This method of Lancichinetti et al. relies on a fitness function that measures the statistical significance of clusters with respect to random fluctuations, and attempts to optimize this fitness function across all clusters. 
Following~\cite{LancichinettiPlos}, the significance measure is defined as the probability of finding the cluster in a network without community structure. The null model used is basically the same as the one adopted by Newman and Girvan in \cite{newman2004finding} to define modularity, {\it i.e.} it is a model that generates random graphs with a given degree distribution. The authors tested their algorithm on different benchmarks (LFR and Girvan-Newman) and real networks (such as the US air transportation network and a word association network), and compared its performance against the best algorithms
currently available (i.e the ones mentioned in the introduction), and found excellent results. Moreover, they showed that OSLOM is also able to recognize the absence, and not simply the presence, of community structure, by testing it on random graphs. This feature of the algorithm plays an important role in the analysis of real world networks, since it is not always the case that community structure is indeed present and it is therefore useful to be able to detect its absence too. 
Therefore, given its versatility and performance with benchmark networks, in this paper we used OSLOM to detect \emph{overlapping} communities present in our \emph{weighted} and \emph{directed} networks.
%For this paper we use OSLOM since it allowed us to detect \emph{overlapping} communities present in our \emph{weighted} and \emph{directed} network, and its authors showed that it performs very well on various types of artificial benchmark graphs and also on several real networks.

@@

Operationally, we expect users to interact with Twitter on a human time scale, and thus the natural one-second time resolution is too fine; since most humans do not write tweets on the time scale of seconds. For this reason, we coarsen each time series by considering non-overlapping time intervals ten minutes in length. For each time interval, we record a 1 if the user has tweeted during that time interval, and a 0 if they have not. Thus, the new coarsened time series now captures whether or not the user has been active on Twitter over any given ten minute time interval in our data set. It should be noted that, as (most) users are not constantly tweeting, these time series are quite sparse. 
%This sparsity will skew the distribution of tweet activity toward being inactive, as the distribution should be to reflect realistic usage statistics.
However, if this measure is to be used in practice a deeper analysis of the effects of binning, the resulting sparsity, and their role in the activity-based community structure should be carried out.

### 2014-11-26 paper-postreview/paper.tex
Took a pass through the paper.
I made minor changes, mostly stylistic.

\title{Followers Are Not Enough: A Question-Oriented Approach to Community Detection in Online Social Networks}

@@

\begin{abstract}
%\begin{quote}
%The Keywords
%Community detection, functional communities, social network analysis, transfer entropy

Community detection in online social networks is typically based on the analysis of the explicit connections between users, such as ``friends" on Facebook and ``followers" on Twitter. But online users often have hundreds or even thousands of such connections, and many of these connections do not correspond to real friendships or more generally to accounts that users interact with. We claim that community detection in online social networks should be question-oriented and rely on additional information beyond the simple structure of the network. The concept of `community' is very general, and different questions such as ``whom do we interact with?" and ``with whom do we share similar interests?" can lead to the discovery of different social groups. In this paper we focus on three types of communities beyond structural communities: activity-based, topic-based, and interaction-based. We analyze a Twitter dataset using three different weightings of the structural network meant to highlight these three community types, and then infer the communities associated with these weightings. We show that the communities obtained in the three weighted cases are highly different from each other, and from the communities obtained by considering only the unweighted structural network. Our results confirm that asking a precise question is an unavoidable first step in community detection in online social networks, and that different questions can lead to different insights about the network under study.
%\end{quote}
\end{abstract}

>>>>

\title{Followers Are Not Enough: A Multifaceted Approach to Community Detection in Online Social Networks
}

@@

\begin{abstract}

In online social media networks, individuals often have hundreds or even thousands of connections, which connect these users not only to friends, associates, and colleagues, but also to news outlets, celebrities, and government organizations. In these complex social networks, a `community' as studied in the social network literature, can have very different meaning depending on the property of the network under study. 
% and different definitions of community such as ``whom do we interact with?" and ``with whom do we share similar interests?" can lead to very different and interesting social groups. 
Taking into account the multifaceted nature of these networks, we claim that community detection in online social networks should also be multifaceted in order to capture all of the different and valuable viewpoints of `community.' In this paper we focus on three types of communities beyond follower-based structural communities: activity-based, topic-based, and interaction-based. We analyze a Twitter dataset using three different weightings of the structural network meant to highlight these three community types, and then infer the communities associated with these weightings. We show that interesting insights can be obtained about the complex community structure present in  social networks by studying when and how these four community types give rise to similar as well as completely distinct community structure.
\\\\

%\begin{quote}
%The Keywords
%Community detection, functional communities, social network analysis, transfer entropy

%Community detection in online social networks is typically based on the analysis of the explicit connections between users, such as ``friends" on Facebook and ``followers" on Twitter. But online users often have hundreds or even thousands of such connections, many of which connect them with news outlets, governmental organizations, etc., in addition to their friends and associates. Because of the multifaceted nature of these networks, we claim that community detection in online social networks should be multifaceted, question-oriented and rely on additional information beyond the simple structure of the network. The concept of `community' is very general, and different questions such as ``whom do we interact with?" and ``with whom do we share similar interests?" can lead to the discovery of different and interesting social groups. In this paper we focus on three types of communities beyond follower-based structural communities: activity-based, topic-based, and interaction-based. We analyze a Twitter dataset using three different weightings of the structural network meant to highlight these three community types, and then infer the communities associated with these weightings. We show that interesting insights can be obtained about the true community structure of a social network by studying when and why these four different community types are disjoint and when they overlap. Community structure that would be missed if only doing a single layer of community detection. 
%%
%We show that the communities obtained in the three weighted cases %are highly different from each other, and from the communities %obtained by considering only the unweighted structural network.
%Our results confirm that asking a precise question is an unavoidable first step in community detection in online social networks, and that different questions can lead to different insights about the network under study.
 %Our results confirm that asking a series of precise question is an unavoidable first step in community detection in online social networks, and that different questions can lead to different insights about the network under study.

%\end{quote}
\end{abstract}
